Risk Perceptions for Wearable Devices

### 2015-04-13 tex-inputs/intro.tex
use PETS formatting; little intro tweaks

Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} that may see significant growth in the near future: one market research company estimates that 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}. With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life.

% Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes}.''

Wearable devices offer many compelling opportunities for benefiting users.  For instance, they could enable more natural, human-centered interface experiences and healthier, fitness-data inspired lifestyles. There will likely be many more applications in the future that take advantage of data captured by wearable devices. However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Even though wearable technology is currently in early stages, we have already seen manifestations of these risks. For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information. Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, and public backlash may have partly contributed to Google's discontinuation of Glass~\cite{1_russell_2014, 16_gross_2014}.

>>>>

Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} with a promising future. 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}. With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life. Wearable devices enable many benefits, ranging from interaction with virtual objects in an augmented reality world to healthier, fitness-data inspired lifestyles.

However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Even though wearable technology is currently in early stages, we have already seen manifestations of these risks. For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information. Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, and public backlash may have partly contributed to Google's discontinuation of Glass~\cite{1_russell_2014, 16_gross_2014}.
